% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVTitle}{Brian Gallew's CV for Nadine Miller}
\newcommand{\CVNote}{CV compiled on {\today} for Nadine Miller}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={Brian Gallew},
%pdfsubject={http://www.example.com/johndoe},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Brian Gallew}

\begin{subtitle}
%\href{https://www.google.com/maps/place/320+Manciano+Way,+Reno,+NV+89521,+USA}
%{320 Manciano Way, Reno, Nevada, 89521, USA}
\par
\href{mailto:resume@gallew.org}
{resume@gallew.org}
\,\BulletSymbol\,
+1\,(775)\,468-8388
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%
%% ABOUT ME %%
%%%%%%%%%%%%%%

\section
{About Me}
{About Me}
{PDF:AboutMe}

Full-stack sysadmin specializing in backups, monitoring and automation.
Strong technical and documentation skills coupled with a desire to learn.
Excellent at communicating with peers and senior management at all skill
levels.  Works well under pressure but prefers to apply engineering
beforehand to prevent problems.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

\textbf{Automation}\par
cfengine, Saltstack, Puppet, Jenkins
\SmallEntryGap

\textbf{Monitoring}\par
Zabbix, Nagios, Open Monitoring Distribution
\SmallEntryGap

\textbf{Backups}\par
Bacula, NetBackup, NetWorker, Amanda, Time Navigator
\SmallEntryGap

\textbf{Data}\par
MySQL, Cassandra, Hadoop, Oracle
\SmallEntryGap

\textbf{Tools}\par
Python, Shell, Perl, Ruby, PHP, Apache, Git
\SmallEntryGap

%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Experience}
{Experience}
{PDF:Experience}

\href{http://www.limelight.com/}
{\textbf{Limelight Networks}},
Tempe, Arizona, USA
\par
Database Engineer IV
\hfill
\DatestampYM{2012}{08} -- Present

\begin{detail}

\BulletItem
Designed and deployed 5 Hadoop clusters using cfengine/Salt and
monitoring by Zabbix and OpenTSDB with HDFS metadata backups done by
Bacula.  One is the basis of Limelight's billing system and thus in-scope
for Sarbanes-Oxley.

\BulletItem
Developed, tested, and executed cfengine deployment of an internal,
geographically aware DNS platform across 6 continents and 150 systems.
Deployments which were previously a multi-hour process were reduced to no
more than 15 minutes of hands-on time.

\BulletItem
Designed and deployed 4 Cassandra clusters, the largest being 48 nodes and
37TB of data spread across 3 continents.  They are fully monitored by
Zabbix, backed up with Bacula, and managed by cfengine.  I also wrote
\href{https://github.com/BrianGallew/cassandra\_tools}{tools} for repair
management and real-time monitoring.  The largest cluster is used as the
directory service which enables Limelight to egress over 8Tbps of customer
data.

\BulletItem
Assisted in the build and day-to-day management of 50 MySQL clusters,
mostly comprised of four-node HA/DR pairs.  Wrote all the Salt states for
the automated build of new clusters, as well as all new Zabbix monitoring.
Managed backups and restores with Bacula.

\BulletItem
Deployed a brand new 700TB Bacula-based backup system with Salt.  All
client configurations are fully automated.  This system backs up both
traditional Unix systems as well as MySQL, MongoDB, and Cassandra.


\BulletItem
MySQL upgrade from multiple versions to 5.5.  Performed a live upgrade of 5
trans-continental MySQL clusters with a combination of circular replication
and read-only replication slaves with no service interruption.

\BulletItem
Wrote, packaged, and deployed tools to perform data collection, system
management, asset management, new datacenter turn-up, backup management,
and management of Zabbix.

\end{detail}
\EntryGap

\href{http://www.copart.com/}
{\textbf{Copart}},
Reno, Nevada, USA
\par
Senior Systems Administrator
\hfill
\DatestampYM{2010}{04} -- \DatestampYM{2012}{08}

\begin{detail}

\BulletItem
Implemented two Puppet installations, one a green field, the other to
existing infrastructure, over 800 systems.  I also wrote custom facts for
Puppet and provided patches to both Puppet and Foreman as I customized them
for our environment or fixed outstanding bugs.

\BulletItem
Supported an online, real-time auction service with customers in more than
55 countries.  Worked to standardize systems, leading to faster roll-out
times.

\BulletItem
Wrote custom provisioning software to integrate with the existing asset
management platform, which I also extended.

\BulletItem
Replaced the existing single-node Nagios installation with a three-node
\href{http://omdistro.org/}{OMD} installtion which provided resilience,
locality, and much more comprehensive monitoring.  I also integrated this
with Puppet to ensure that every deployed system was monitored during its
entire lifecycle.

\BulletItem
Implemented a push-button deployment system with Jenkins.  This turned a
very human-driven, hour-long deployment procedure for 2-3 staff into a
single form in Jenkins which typically completed all of the tasks in 10
minutes.

\end{detail}
\EntryGap


\href{http://qatar.cmu.edu/}
{\textbf{Carnegie Mellon University - Qatar}},
Doha, Qatar
\par
Research Systems Manager
\hfill
\DatestampYM{2009}{04} -- \DatestampYM{2010}{04}

\begin{detail}
  

\BulletItem
Implemented an IBM Blue Cloud (beta) system for Hadoop research.  This
included altering the underlying deployment software to work around bugs
and design flaws in the delivered system.

\BulletItem
Supported the development of a curriculum to teach Carnegie Mellon students
how to use distributed systems to solve large data problems using Hadoop.

\BulletItem
Implemented centralized systems configuration management via Puppet.

\BulletItem
Worked with faculty in evaluating their infrastructure needs and the best
methodologies to provide them with a reliable research platform.

\end{detail}
\EntryGap


\href{http://qatar.cmu.edu/}
{\textbf{Carnegie Mellon University - Qatar}},
Doha, Qatar
\par
Systems Manager
\hfill
\DatestampYM{2006}{04} -- \DatestampYM{2009}{04}

\begin{detail}
\BulletItem
Sole sysadmin having responsibility for all production systems, including
web services, email, distributed storage, networked file systems, backup,
maintenance, accounts, provisioning, and physical infrastructure serving a
campus of 400 students with another 100 staff and faculty.

\BulletItem
Implemented VMware VirtualCenter and converted 95\% of our infrastructure
to virtual machines on SAN storage, reducing our footprint from 350+
physical servers to fewer than 80, while increasing not only the resilience
of the services we offered but adding capacity.

\BulletItem
Migrated all services between from one DC to another with no interruption
in user services.

\BulletItem
Added redundancy and near-real-time recovery mechanisms where appropriate.

\BulletItem
Replaced an Amanda-based backup system with Time Navigator, extending it to
cover Oracle services and MySQL services, and using DataDomain storage for
deduplication, compression, and off-site replication.

\BulletItem
Replaced more than 20 individually configured and managed MySQL servers
with a MySQL service with replication and fail-over capabilities.

\BulletItem
Implemented systems monitoring through log file consolidation and
mining. Extended the automated monitoring system to handle new services.

\BulletItem
Worked with the design team on the layout, equipment, and management of a
new data center.

\BulletItem
Built and deployed network security tools (Argus and Snort). Created
hardened system configurations and deployed them via a custom provisioning
system.

\end{detail}
\EntryGap

\href{http://www.cmu.edu/}
{\textbf{Carnegie Mellon University}},
Pittsburgh, Pennsylvania, USA
\par
Senior System Administrator
\hfill
\DatestampYM{1992}{05} -- \DatestampYM{2006}{04}

\begin{detail}

\BulletItem
Managed a team of three sysadmins whose responsibilities included all
administrative systems (Student Information System, Human Resources
Information System, Property Accounting System, Oracle Financials).

\BulletItem
Responsible for the selection, purchase, and implementation of all the
hardware and software supporting the administrative systems.

\BulletItem
Developed Apache modules in support of online registration.

\BulletItem
Deployed a live, tested disaster recovery site in all details (power,
cooling, networking, equipment, 40TB data replication) using Sun, HP, and Dell
servers and Xiotech storage.  Not only did this provide resilience for all
our administrative systems (including Oracle Financials), the design
enabled us to do development on up-to-date datasets whicn in turn provided
continuous assurance that replication was functioning correctly.

\BulletItem
Primary engineer for the migration of production applications between 8
different operating systems running on 7 different vendor platforms (Sun,
HP, DG, DEC, Sequent, IBM, Dell).

\BulletItem
Systems architect for the \$18M Oracle Financials implementation.

\BulletItem
Converted the previous open access network model to a more restricted one
where only explicitly exported services were available to customers, while
enabling developers to continue to work productively.

\BulletItem
Managed local response to security incidents while coordinating with the
central information security team.

\end{detail}
\EntryGap


%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.cmu.edu/}
{\textbf{Carnegie Mellon University}},
Pittsburgh, Pennsylvania, USA
\par
Bachelor of Science (B.S.) in
\href{http://www.ece.cmu.edu/}
{Computer Engineering}
\hfill

%% \href{http://www.goarmy.com/}
%% {\textbf{United States Army}},
%% USA, Germany, Korea
%% \par
%% Communication Specialist/Intel Analyst
%% \hfill
%% \DatestampYM{1985}{06} -- \DatestampYM{1998}{06}

%% \begin{detail}
%% \BulletItem
%% Managed all aspects of the company tactical operations center, including communcations, security, maps, tracking of friendly and enemy soldiers, and defense.
%% \BulletItem
%% Managed training and testing schedules for the entire company.
%% \BulletItem
%% Developed and deployed database applications for unit management at both the company and battalion/squadron level.

%% \end{detail}
%% \EntryGap

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\begin{flushright}
\scriptsize%
[\textit{\CVNote}]%
\hspace{2.0mm}\null
\end{flushright}

\label{LastPage}~
\end{document}
